Maximum Entropy Spectral Analysis: a case study

### 2021-02-21 paper/mesa.tex

\begin{equation}\label{eq:MESApsd}
    S(f) = \frac{P_N \Delta t}{\left(\sum_{s=0}^N a_s z^s\right)\left(\sum_{s = 0}^N a^*_s z^{-s}\right)}, 
\end{equation}
with $\Delta t$ the sampling interval, $z=\exp{(2\pi i f)}$, $a_0$ = 1 and the coefficients $P_N$ and $a_i (i \neq 0)$ to be determined. The details of the derivation and the actual values of the coefficients $a_i$ can be found in appendix \ref{sec:MESA_solution}.

>>>>

\begin{equation}\label{eq:MESApsd}
    S(f) = \frac{P_N \Delta t}{\left(\sum_{s=0}^N a_s z^s\right)\left(\sum_{s = 0}^N a^*_s z^{-s}\right)}, 
\end{equation}
with $\Delta t$ the sampling interval, $z=\exp{(2\pi i f\Delta t)}$, $a_0$ = 1 and the coefficients $P_N$ and $a_i (i \neq 0)$ to be determined. The details of the derivation and the actual values of the coefficients $a_i$ can be found in appendix \ref{sec:MESA_solution}.
